### 2015-04-06 cug_paper/01_introduction.tex
Paper: Section 2 is now at rough draft stage
Fix single-quotes
To single quote foo, use `foo' instead of 'foo'

In some of these cases, we might want to drop single-quotes and use
\emph{}, \textbf{}, or \texttt{}

In most HPC applications, filesystem writes typically follow a very 'bursty' pattern. That is, there will be long periods with no file output while the application is in a compute phase, followed by a period of intense output and no computation when the application writes its checkpoint or output files.  Also, at ORNL, the filesystem is a shared resource and other users will also be putting a varying load on it. This means that the performance that a user sees at any given time will likely vary dramatically.

@@

Having a sufficiently large write-back cache would alleviate both of these problems. Assuming the cache is large enough, then the 'bursty' nature of the output pattern can be smoothed out since there will be time for the traffic to drain from the cache before the next burst arrives. Equally importantly, write performance should be more predictable. From the application's point of view, write speed is only limited by how fast data can be copied into the cache, and that is not effected by outside influences. The GPU memory and integer cores can be used to implement such a cache without taking resources away from the main application.

>>>>

In most HPC applications, filesystem writes typically follow a very `bursty' pattern. That is, there will be long periods with no file output while the application is in a compute phase, followed by a period of intense output and no computation when the application writes its checkpoint or output files.  Also, at ORNL, the filesystem is a shared resource and other users will also be putting a varying load on it. This means that the performance that a user sees at any given time will likely vary dramatically.

@@

Having a sufficiently large write-back cache would alleviate both of these problems. Assuming the cache is large enough, then the `bursty' nature of the output pattern can be smoothed out since there will be time for the traffic to drain from the cache before the next burst arrives. Equally importantly, write performance should be more predictable. From the application's point of view, write speed is only limited by how fast data can be copied into the cache, and that is not effected by outside influences. The GPU memory and integer cores can be used to implement such a cache without taking resources away from the main application.

### 2015-04-06 cug_paper/02_design.tex
Fix single-quotes
To single quote foo, use `foo' instead of 'foo'

In some of these cases, we might want to drop single-quotes and use
\emph{}, \textbf{}, or \texttt{}

Note that the data has not made it out to the filesystem yet; it's just sitting in GPU memory.  Upon receiving the 'write done' message from the application, the daemon now knows it's free to

@@

From the application's point of view, the write has completed once the 'write done' message has been successfully sent.

Once the applications sends the 'write done' message

@@

\todo[inline]{Need an introduction paragraph for this subsection.}
The CUDA runtime can be configured to limit access to the GPU to a single thread, to multiple threads from a single process or to multiple threads from multiple processes.  On Titan, if no special options are given to qsub, the CUDA runtime will be configured for a single thread.  Since software described in this paper requires access to the GPU from multiple processes, users must switch to the appropriate compute mode.  This is done by passing the flag "-l feature=gpudefault" to qsub.\footnote{It may seem strange to have to explicitly switch to a mode called 'gpudefault'.  The naming scheme comes from the CUDA documentation.  On a standard CUDA install, the GPU would in fact default to allowing access from multiple processes.  Titan is configured differently, however.  Thus the need to explicitly tell qsub to switch to the 'default' mode.}

>>>>

Note that the data has not made it out to the filesystem yet; it's just sitting in GPU memory.  Upon receiving the `write done' message from the application, the daemon now knows it's free to

@@

From the application's point of view, the write has completed once the `write done' message has been successfully sent.

Once the applications sends the `write done' message

@@

\todo[inline]{Need an introduction paragraph for this subsection.}
The CUDA runtime can be configured to limit access to the GPU to a single thread, to multiple threads from a single process or to multiple threads from multiple processes.  On Titan, if no special options are given to qsub, the CUDA runtime will be configured for a single thread.  Since software described in this paper requires access to the GPU from multiple processes, users must switch to the appropriate compute mode.  This is done by passing the flag "-l feature=gpudefault" to qsub.\footnote{It may seem strange to have to explicitly switch to a mode called `gpudefault'.  The naming scheme comes from the CUDA documentation.  On a standard CUDA install, the GPU would in fact default to allowing access from multiple processes.  Titan is configured differently, however.  Thus the need to explicitly tell qsub to switch to the `default' mode.}
